%-------------------------
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------------
%%%%%%  NOW the GOOD STUFF  %%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {} & \textbf{Email} : \href{mailto:rajat.gupta99924@gmail.com}{rajat.gupta99924@gmail.com}\\
  \textbf{\href{https://z3ta.me/}{\huge Rajat Gupta}} & \textbf{Mobile} {: +91-9047393679}\\
   \textbf{Blog:} \href{https://z3ta.me/}{z3ta.me} & \textbf{LinkedIn:} \href{https://linkedin.com/in/rjt-gupta}{linkedin.com/in/rjt-gupta}\\
  {} & \textbf{GitHub:} \href{https://github.com/rjt-gupta}{github.com/rjt-gupta}\\
  

\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Relevant Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google Summer of Code}{}
      {The Honeynet Project - SNARE/TANNER}{May 2019 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Worked on an advanced reactive \textbf{Web Application Honeypot} to detect malicious attacks. It sends the HTTP events to tanner which analyzes them. Also, worked on increasing coverage for cloner and other utilities. }
        \resumeItem{}
          {Tanner is a remote data analysis and classification service used to compose the response then served by SNARE events. I worked on the execution of attacks using custom \textbf{docker} images and \textbf{php sandbox.}}
        \resumeItem{}
        {Developed emulators to support \textbf{Template Injection, PHP Object Injection and XXE Injection} vulnerabilities.}
        \resumeItem{}
        {Implemented a helper utility for \textbf{Aiodocker} for managing docker asynchronously.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, India}
      {Bachelor of Technology in Computer Science;  CGPA: 9.16/10.00}{July. 2017 -- 2021}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Mitmproxy: Open Source Contribution - \textit{An interactive TLS-capable intercepting proxy}\\}{\hspace{152mm}\textit{Jan 2019 - Present}}
    \resumeItemListStart{}
        \resumeItem{}
        {Actively contribute to core proxy and its add-ons, has over \textbf{16,000 stars} on GitHub.}
        \resumeItem{}
        {Implemented an encoder for parsing multipart/form-data during image uploads.}
        \resumeItem{}
        {Added support for Non-ASCII characters in URL while parsing and extended filtering flows to filter Non-ASCII characters like Cyrillic alphabets etc.}
    \resumeItemListEnd

    \resumeSubItem{Vault: Open Source Contribution - \textit{Swiss Army Knife for hackers}}{\hspace{50mm}\textit{Dec 2018}}
      \resumeItemListStart
        \resumeItem{}
      {Contributed to vault as a part of IIT Kharagpur Winter of Code'18.}
      \resumeItem{}
      {Implemented new attack modules and check functions in \textbf{Python3}.}
    \resumeItemListEnd

    \resumeSubItem{Decentralized Blockchain}{\hspace{123mm}\textit{Oct 2018}}
    \resumeItemListStart{}
        \resumeItem{}
        {Created an API for decentralized blockchain prototype using \textbf{JavaScript}}
        \resumeSubItem{}
        {Features a consensus algorithm (\textbf{longest chain algorithm}) to verify the network nodes have valid data, a broadcasting system to keep the data across network nodes synchronized along with a \textbf{proof-of-work} mechanism.}
    \resumeItemListEnd

    \resumeSubItem{ANTON: \textit{Remote Administration tool}}{\hspace{100mm}\textit{Mar 2018}}
      \resumeItemListStart
        \resumeItem{}
      {Developed exploit modules to steal saved chrome passwords, decrypted using windows API \textbf{CryptUnprotectData} and transfer over HTTP/TCP reverse shells including text to speech recognition module using \textbf{Python3}.}
      \resumeItem{}
      {Achieved \textbf{1/66 detection ratio from virus total} on the final compiled malware executable.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%---------Achievements-------------------
\section{Achievements}
    
    \resumeItemListStart
        \resumeItem{CyBRICS CTF 2019: }
        {Finished among top 25 teams in Qualifiers and got selected for \textbf{Onsite Finals at St. Petersburg, Russia}.}
        \resumeSubItem{HackTheBox: }
        {Organized a University level CTF competition in which created \textbf{web and buffer overflow challenges} which received total participation of more than 500 teams.}
        \resumeItemListEnd
  
%-----------VOLUNTEERING-----------------
\section{Volunteering}
   \resumeSubHeadingListStart 
    \resumeSubheading
      {Computer Society of India}{Vellore, TN}
      {Core Committee Member}{Nov 2017 - May 2019}
      \iffalse   % Commenting this part
      \resumeItemListStart
        \resumeItem{HackTheBox: }
        {Conducted a University level CTF competition in which created \textbf{web and buffer overflow challenges} which received total participation of more than 500 players.}
        \resumeItem{DEVSPACE: }
          {Worked to organize the flagship 3-day event conducting seminars, workshops and a hackathon which witnessed more than 700 participants.}
        \resumeItem{Speaker: }
          {Conducted workshops and events introducing Bug Bounties, Web Penetration Testing and Open Source.}
      \resumeItemListEnd
      \fi

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills and Interests}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages: }{
       Python, Javascript, C/C++ 
    }
    \resumeSubItem{Technologies: }{
      Node.js, Django, MongoDB, Docker, Git, \LaTeX
    }
    \resumeSubItem{Tools: }{
      Burp Suite, Metasploit, Mitmproxy, Nmap, Wireshark, Immunity Debugger. 
    }

  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
